---
title: "code_submission"
author: "Yuchen Chen"
date: "2026-03-08"
output: pdf_document
---

# Set up 

```{r set up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(reshape2)
library(ggrepel)
library(viridis)
library(EloRating)
library(ggpubr)
library(lsmeans)
library(igraph)
library(ggnetwork)
library(kableExtra)
library(assortnet)
library(broom)
library(purrr)
library(lme4)
library(patchwork) 
library(performance)
library(gtsummary)
library(glmmTMB)
library(readr)
library(statnet) 
library(magick)
library(ggplot2)
library(cowplot)
library(car)
library(reshape2)
library(officer)
library(flextable)


setwd("/Users/tiffsmac/Desktop/hobson/sex comparison project/monk.sex.comparison/submission")

data_location <- "/Users/tiffsmac/Desktop/hobson/sex comparison project/monk.sex.comparison/submission/data"
figure_output_folder <- "/Users/tiffsmac/Desktop/hobson/sex comparison project/monk.sex.comparison/submission/figures"
table_output_folder <- "/Users/tiffsmac/Desktop/hobson/sex comparison project/monk.sex.comparison/submission/tables"


matrix.please<-function(x) {
        m<-as.matrix(x[,-1])
        rownames(m)<-x[,1]
        m
}

matrix.please <- function(df) {
  all_ids <- union(df$actor, df$subject)

  df_wide <- df %>%
    select(actor, subject, nevents) %>%
    complete(actor = all_ids, subject = all_ids, fill = list(nevents = 0)) %>%
    pivot_wider(names_from = subject, values_from = nevents, values_fill = 0) 

  m <- as.matrix(df_wide[,-1])
  rownames(m) <- df_wide$actor
  m
}

```


# Load data
```{r}
all.aggWsex <-  read_csv(paste0(data_location,"/data_submission.csv"))

bird.list <-  read_csv(paste0(data_location,"/bird_submission.csv"))

```

# Separate to different groups
```{r separate into groups}
split_dfs <- split(all.aggWsex, all.aggWsex$groupID)

names(split_dfs)  
```

#Calculate rank

## Load springrank code from Cate/Dan 

```{r springrank}
library(igraph)
library(Matrix)
library(Rlinsolve)

spring_rank <- function(A, alpha = 0, l0 = 1.0, l1 = 1.0,
                        shift = TRUE, solver = Rlinsolve::lsolve.bicgstab) {
  #' Core function for calculating SpringRank.
  #' Default parameters follow stanadard model.
  #'
  #' @param A The adjacency matrix of the graph. This should be a sparse dgCMatrix;
  #' if it isn't it will be coerced to a dgCMatrix.
  #' @param alpha Controls the impact regularization term.
  #' @param l0 Regularization spring's rest length.
  #' @param l1 Interaction springs' rest length.
  #' @param shift (Optional, default TRUE) normalize such that the lowest-ranked
  #'  node has a SpringRank value of zero.
  #' @param solver (Optional, default Rlinsolve::bicgstab) your preferred
  #' solver for Ax=B. Should be able to handle dgCMatrix sparse matrices.
  #' if the solve is not from Rlinsolve may throw a spurious warning for
  #' unused parameters.
  #'
  #' @return A vector of SpringRank scores for each node. Sort or order the
  #' vector for ordinal rankings of each node.
  
  if (class(A) == "matrix") {
    # coerce dense matrix to sparse matrice so the user doesn't have to.
    A <- as(Matrix(A, sparse = TRUE, doDiag = FALSE), "dgCMatrix")
  } else {
    # confirm it's the right kind of sparse matrix. might throw an error
    # if it's one of the less common sparse matrix types.
    A <- as(A, "dgCMatrix")
  }
  
  N <- dim(A)[1]
  k_in <- colSums(A)
  k_out <- rowSums(A)
  One <- as(Matrix(rep(1, N)), "dgCMatrix")
  C <- A + t(A)
  
  D1 <- as(Matrix(0, ncol = N, nrow = N), "dgCMatrix")
  D2 <- as(Matrix(0, ncol = N, nrow = N), "dgCMatrix")
  
  for (i in 1:N) {
    D1[i, i] <- k_out[i] + k_in[i]
    D2[i, i] <- l1 * (k_out[i] - k_in[i])
  }
  
  if (alpha != 0) {
    print("assuming invertible matrix")
    
    B = One * l0 + D2 %*% One
    A_ = alpha * diag(nrow = N, ncol = N) + D1 - C
  } else {
    print("fixing a rank degree of freedom")
    
    C <- C +
      matrix(rep(A[N,] , times = N),
             ncol = N,
             nrow = N,
             byrow = T) +
      matrix(rep(A[, N], times = N),
             ncol = N,
             nrow = N,
             byrow = T)
    
    D3 <- as(Matrix(0, ncol = N, nrow = N), "dgCMatrix")
    for (i in 1:N) {
      D3[i, i] <- l1 * (k_out[N] - k_in[N])
    }
    
    B <- D2 %*% One + D3 %*% One
    A_ <- D1 - C
  }
  
  rank <- solver(A_, B, verbose = F)
  if (class(rank) == "list") {
    rank <- rank$x # accomodates both Rlinsolve and Matrix solves
  }
  
  if (shift) {
    rank <- rank - min(rank)
  }
  
  # coerce matrix to vector, so we can use names()
  rank <- rank[,1]
  names(rank) <- colnames(A)
  return(rank)
}


spring_rank_network <- function(N, beta, alpha, K, l0 = 0.5, l1 = 1.0) {
  #' Generative model for SpringRank. Builds a weighted graph with self-loops.
  #' The model first generates node scores using a normal distribution, then
  #' generates edges (and edge weights) from a Poisson distribution with mean
  #' equal to the energy of the system.
  #'
  #' @param N The number of nodes.
  #' @param beta Inverse temperature, a noise parameter.
  #' @param alpha Variance of the Normal prior.
  #' @param K The average degree of the network.
  #' @param l0 Prior spring's rest length.
  #' @param l1 Interaction spring's rest length.
  #'
  #' @return A directed graph (potentially weighted, potentially containing
  #' self-loops)
  
  scores <- rnorm(N, l0, 1/sqrt(alpha*beta))
  Z <- 0
  for (i in 1:N) {
    for (j in 1:N) {
      Z <- Z + exp(-0.5 * beta * (scores[i] - scores[j] - l1)^2)
    }
  }
  C <- (K*N)/Z
  
  # for loops are slow in R so make a matrix of element-wise subtractions,
  # each element i, j being scores[i]-scores[j]
  # basically, trading off increased memory usage (dense matrix) for speed.
  scores_mat <- matrix(1, length(scores), 1) %*% t(scores)
  scores_mat <- scores_mat - scores - l1
  H <- .5 * scores_mat^2
  lambda <- C * exp(-1*beta*H)
  A <- rpois(length(scores)^2, lambda) %>% matrix(nrow = dim(lambda)[1])
  
  return(graph_from_adjacency_matrix(A, mode = "directed", weighted = "weight"))
}
```


## Calculate springrank power, ordinal rank, rule breaking etc for each group

```{r calculate rank}

compute_springrank <- function(df) {
  
  agg.el <- df %>% ungroup()

agg.el <- agg.el %>% select(actor, subject, subject.sex, actor.sex, nevents)

    g <- graph.data.frame(agg.el)
    g.adj <- get.adjacency(g, sparse = TRUE, attr='nevents')
    rank_spring <- as.data.frame(spring_rank(g.adj))
    
    
    rank_spring$birdID <- rownames(rank_spring)
    colnames(rank_spring) <- c("springrank_value", "birdID")
    rank_spring <- rank_spring %>% arrange(desc(springrank_value))
    rank_spring$rank_springrank <- seq(1:nrow(rank_spring))

    
     rank_subjects <- rank_spring %>%
    rename(
      subject.power = springrank_value,
      subject = birdID,
      subject.rank = rank_springrank
    )
  
  rank_actors <- rank_spring %>%
    rename(
      actor.power = springrank_value,
      actor = birdID,
      actor.rank = rank_springrank
    )
  
  
    df <- df %>%
      left_join(rank_subjects, by = "subject") %>% 
      left_join(rank_actors, by = "actor") 
    
    df <- df %>% 
      mutate(power.diff = actor.power - subject.power,
             rank.diff = actor.rank - subject.rank)
}


split_dfs_Wrank <- map(split_dfs, compute_springrank)

G1 <- compute_springrank(split_dfs[["G1"]])

G2 <- compute_springrank(split_dfs[["G2"]])

G3 <- compute_springrank(split_dfs[["G3"]])

G4 <- compute_springrank(split_dfs[["G4"]])

G5 <- compute_springrank(split_dfs[["G5"]])

```

# Data cleaning

datasets that we are using:

rank_df_all : 50 rows of birds with power and sex

combined_df_Wrank_sexb : 248 rows of dyadic interactions with power and sex

```{r data cleaning}
combined_df_Wrank_sexb <- bind_rows(
  "G1" = G1,
  "G2" = G2,
  "G3" = G3,
  "G4" = G4,
  "G5" = G5,
  .id = "groupID"
)

combined_df_Wrank_sexb %>% 
  group_by(groupID) %>% 
  summarise(sumagg = sum(nevents)) %>% 
  ungroup()

df1_all <- combined_df_Wrank_sexb %>%
  distinct(birdID = actor, rank = actor.rank, power = actor.power, groupID = groupID, sex = actor.sex)

df2_all <- combined_df_Wrank_sexb %>%
  distinct(birdID = subject, rank = subject.rank, power = subject.power, groupID = groupID, sex = subject.sex)

rank_df_all <- bind_rows(df1_all, df2_all) %>%
  distinct(birdID, .keep_all = TRUE)
  

```


#1.Individual Level

##Plotting

Plot - 5 groups

agg_by_actor_group : 50 rows of birds with total aggression events, sex, and power

```{r individual plot, fig.width = 10, fig.height = 5}
colrs <- c("Female" = "#F8766D", "Male" = "#00BFC4")

#Aggregate nevents per actor (bird) within each group
agg_by_actor_group <- combined_df_Wrank_sexb  %>%
  group_by(groupID, actor, actor.sex) %>%
  summarise(total_events = sum(nevents), .groups = "drop")

#There is a bird never becomes aggressor
agg_by_actor_group  <- rank_df_all %>% 
  left_join(agg_by_actor_group, join_by("birdID"=="actor") ) %>% 
  mutate(groupID = coalesce(groupID.x, groupID.y),
         sex = coalesce(sex, actor.sex)) %>% 
  select(birdID, rank, power, groupID, sex, total_events) %>% 
  mutate(total_events = if_else(is.na(total_events), 0, total_events))

#Boxplot by group and sex showing total aggression per bird
sex_boxplot_group <- ggboxplot(agg_by_actor_group, x = "groupID", y = "total_events", color = "sex", add = "jitter") +
  scale_color_manual(values = colrs) + 
  #theme_minimal() +
  labs(y = "Number of aggression", color = "Actor sex", x ="Group") +
  scale_x_discrete(position = "top",
                   labels = c("G1","G2", "G3", "G4", "G5" ))+
    theme(legend.position = "bottom",
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 13),
        axis.title.x = element_text(size = 14),
        axis.title.x.top = element_text(size = 14,margin = margin(b = 12)),
        axis.text.x = element_text(size = 14),
        legend.text = element_text(size = 13),
        legend.title = element_text(size = 13))+
  theme(legend.position = c(0.85, 0.7),
        legend.box.background = element_rect(color = "black", fill = "white", linewidth = 0.2),
        legend.key.size = unit(0.5, 'cm'))+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.line.x.top = element_line(color = "black"),
  axis.ticks = element_line(color = "black"),
  axis.line = element_blank()
)

sex_boxplot_group

ggsave(file.path(figure_output_folder, "sex_boxplot_group.jpeg"), 
       sex_boxplot_group, 
       device = "jpeg", 
       width = 15, height = 10, units = "cm")
 
```


Plot - all together

```{r individual plot all together,fig.width=5, fig.height=5}
#Boxplot all groups combined, by sex, total aggression per bird
sex_boxplot_all <- ggboxplot(agg_by_actor_group, x = "sex", y = "total_events", color = "sex", add = "jitter") +
  scale_color_manual(values = colrs) + 
  theme_minimal() +
 theme(legend.position = "none",
    axis.text.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 13))+
  labs(y = "Number of aggression", x ="") +
   theme(
    panel.grid.major = element_blank() ,
    panel.grid.minor = element_blank()
  )+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.line.x.bottom = element_line(color = "black"),
  axis.ticks = element_line(color = "black"),
  axis.line = element_blank()
)

sex_boxplot_all

ggsave(file.path(figure_output_folder, "sex_boxplot_all.jpeg"), 
       sex_boxplot_all, 
       device = "jpeg", 
       width = 10, height = 10, units = "cm")

```


Get proportions within group

agg_by_actor_group : 50 rows of birds with total aggression events, proportions of aggression, sex, and power

```{r get the propotion within group}
### add group proportion
agg_by_actor_group <- agg_by_actor_group %>% 
  group_by(groupID) %>% 
  mutate(prop_agg = total_events/sum(total_events))

```


Plot 5 group within-group proportion

```{r individual plot with propotions,fig.width=5, fig.height=5}
#Boxplot all groups combined, by sex, total aggression per bird
sex_boxplot_all_prop <- ggboxplot(agg_by_actor_group, x = "sex", y = "prop_agg", color = "sex", add = "jitter") +
  scale_color_manual(values = colrs) + 
  theme_minimal() +
  theme(legend.position = "none",
    axis.text.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 13))+
  labs(y = "Proportion of aggression", x = "") +
   theme(
    panel.grid.major = element_blank() ,
    panel.grid.minor = element_blank()
  )+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.line.x.bottom = element_line(color = "black"),
  axis.ticks = element_line(color = "black"),
  axis.line = element_blank()
)
  
sex_boxplot_all_prop

ggsave(file.path(figure_output_folder, "sex_boxplot_all_prop.jpeg"), 
       sex_boxplot_all_prop, 
       device = "jpeg", 
       width = 10, height = 10, units = "cm")

```


Combine three individual level plots

```{r individual plot with proportions all together,fig.width=10, fig.height=5}

sex_boxplot_combined_complete <- sex_boxplot_group /
  (sex_boxplot_all | sex_boxplot_all_prop) +
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(face = "bold", size = 16))

sex_boxplot_combined_complete

ggsave(file.path(figure_output_folder, "sex_boxplot_combined_complete.tiff"), 
       sex_boxplot_combined_complete, 
       device = "tiff", 
       width = 18, height = 16, units = "cm")
```


## Analysis 

5 groups separate T test
```{r individual T test}
split_agg <- split(agg_by_actor_group, agg_by_actor_group$groupID)

# check before fitting
normality_test <- map(split_agg, ~ shapiro.test(.x$total_events))

variance_test <- map(split_agg, ~ leveneTest(total_events ~ sex, data = .x))

normality_test_table <- map_df(normality_test, tidy, .id = "groupID")

normality_test_table <- normality_test_table %>%
  mutate(across(where(is.numeric), ~ signif(.x, 2)),
         groupID = c("G1", "G2", "G3", "G4", "G5")) %>% select(-method)

# save the check 
normality_test_table

set_flextable_defaults(
  font.size = 10, theme_fun = theme_vanilla,
  padding = 6)

flextable(normality_test_table) %>% 
  save_as_docx( path = paste0(table_output_folder,"/normality_test_table.docx"))

# fit the model
models_sep <- map(split_agg, ~ wilcox.test(total_events ~ sex, data = .x))

wtest_individual_sep <- map_df(models_sep, tidy, .id = "groupID")

wtest_individual_sep  <- wtest_individual_sep %>%
  mutate(across(where(is.numeric), ~ signif(.x, 2)),
         groupID = c("G1", "G2", "G3", "G4", "G5")) %>% select(-method, -alternative)

wtest_individual_sep

# save the model result
flextable(wtest_individual_sep) %>% 
  save_as_docx( path = paste0(table_output_folder,"/wtest_individual_sep.docx"))

write_csv(wtest_individual_sep, file = file.path(table_output_folder, "wtest_individual_sep.csv"))

```

5 groups all together GLMM

```{r individual all together GLM}

#with count data, negative binomial 

individual_model_all_nb1 <- glmmTMB(total_events ~ sex + (1 | groupID), 
                     family = nbinom1, data = agg_by_actor_group)

individual_model_all_nb2 <- glmmTMB(total_events ~ sex + (1 | groupID), 
                     family = nbinom2, data = agg_by_actor_group)

AIC(individual_model_all_nb1 , individual_model_all_nb2 ) # not a big differences

aic_table <- as.data.frame(AIC(individual_model_all_nb1, individual_model_all_nb2))
flextable(aic_table) %>% 
   save_as_docx( path = paste0(table_output_folder,"/AIC_individual_model_comparison.docx"))

#individual_model_all_nb2 is slightly a better fit

summary(individual_model_all_nb1)
summary(individual_model_all_nb2)

r2(individual_model_all_nb1)
r2(individual_model_all_nb2)

individual_model_all_nb1_summary <- summary(individual_model_all_nb1)
individual_model_all_nb2_summary <- summary(individual_model_all_nb2)

# save the model results

individual_model_all_nb1_summary <- capture.output(summary(individual_model_all_nb1))
writeLines(individual_model_all_nb1_summary, file.path(table_output_folder, "individual_model_all_nb1_summary.txt"))

doc <- read_docx()
for(line in individual_model_all_nb1_summary){doc <- body_add_par(doc, line, style = "Normal")}
print(doc,target = file.path(table_output_folder,"individual_model_all_nb1_summary.docx"))

summary(individual_model_all_nb1)$coefficients$cond %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Predictor") %>% 
  flextable() %>% 
  colformat_double(digits = 3) %>% 
  add_footer_lines(
    "Estimate = log-scale coefficient; Std. Error = standard error; z value = Wald z statistic; Pr(>|z|) = p-value."
  ) %>% 
  autofit() %>% 
  save_as_docx(
    path = file.path(table_output_folder, "individual_model_all_nb1_estimates.docx")
  )

individual_model_all_nb2_summary <- capture.output(summary(individual_model_all_nb2))
writeLines(individual_model_all_nb2_summary, file.path(table_output_folder, "individual_model_all_nb2_summary.txt"))

doc <- read_docx()
for(line in individual_model_all_nb2_summary){doc <- body_add_par(doc, line, style = "Normal")}
print(doc,target = file.path(table_output_folder,"individual_model_all_nb2_summary.docx"))

summary(individual_model_all_nb2)$coefficients$cond %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Predictor") %>% 
  flextable() %>% 
  colformat_double(digits = 3) %>% 
  add_footer_lines(
    "Estimate = log-scale coefficient; Std. Error = standard error; z value = Wald z statistic; Pr(>|z|) = p-value."
  ) %>% 
  autofit() %>% 
  save_as_docx(
    path = file.path(table_output_folder, "individual_model_all_nb2_estimates.docx")
  )

#check the model
individual_model_all_nb1_diagnostics_plot <- check_model(individual_model_all_nb1, title_size = 8, base_size =7)
individual_model_all_nb1_diagnostics_plot

individual_model_all_nb2_diagnostics_plot <- check_model(individual_model_all_nb2, title_size = 8, base_size =7)
individual_model_all_nb2_diagnostics_plot

# saving the plot
tiff(file = file.path(figure_output_folder, "individual_model_all_nb1_diagnostics.tiff"), 
     width = 18, height = 18, units = "cm", res = 300)

print(individual_model_all_nb1_diagnostics_plot)

dev.off()

tiff(file = file.path(figure_output_folder, "individual_model_all_nb2_diagnostics.tiff"), 
     width = 18, height = 18, units = "cm", res = 300)

print(individual_model_all_nb2_diagnostics_plot)

dev.off()

#with proportion data, beta regression 

individual_model_all_beta_complete <- glmmTMB(
  prop_agg ~ sex ,#+ (1 | groupID),         
  zi = ~ 1,                              
  family = beta_family(),                 
  data = agg_by_actor_group
)

summary(individual_model_all_beta_complete)
r2(individual_model_all_beta_complete)

# save the model results

individual_model_all_beta_complete_summary <- capture.output(summary(individual_model_all_beta_complete))
writeLines(individual_model_all_beta_complete_summary, file.path(table_output_folder, "individual_model_all_beta_complete_summary.txt"))

doc <- read_docx()
for(line in individual_model_all_beta_complete_summary){doc <- body_add_par(doc, line, style = "Normal")}
print(doc,target = file.path(table_output_folder,"individual_model_all_beta_complete_summary.docx"))

summary(individual_model_all_beta_complete)$coefficients$cond %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Predictor") %>% 
  flextable() %>% 
  colformat_double(digits = 3) %>% 
  add_footer_lines(
    "Estimate = logit-scale coefficient; Std. Error = standard error; z value = Wald z statistic; Pr(>|z|) = p-value."
  ) %>% 
  autofit() %>% 
  save_as_docx(
    path = file.path(table_output_folder, "individual_model_all_beta_complete_estimates.docx")
  )

#check the model
individual_model_all_beta_complete_diagnostics_plot <- check_model(individual_model_all_beta_complete, title_size = 8, base_size =7)
individual_model_all_beta_complete_diagnostics_plot

# saving the plot
tiff(file = file.path(figure_output_folder, "individual_model_all_beta_complete_diagnostics.tiff"), 
     width = 18, height = 18, units = "cm", res = 300)

print(individual_model_all_beta_complete_diagnostics_plot)

dev.off()

```


#2.Dyad Level

## Permutation 

```{r create dyad color}
colrs3 <- c(
            "same sex"="chocolate", 
            "opposite sex"="dimgray")

```

##2 dyad types

2 dyad type permutation test 
```{r permutation 2 dyad types}
set.seed(123)

sex.list <- c("Female", "Female","Female","Female","Female",
              "Male", "Male","Male","Male","Male")

sex.list <- as.data.frame(sex.list)

dyad_perm <- function(df, group_name){

  observed <- df %>%
    group_by(dyad.sex3) %>%
    summarise(mean_events = mean(nevents), .groups = "drop")

t <- 5000
perm_results <- matrix(0, nrow = t, ncol = 2)
colnames(perm_results) <- c("same sex",  "opposite sex")

for (i in 1:t) {
    rows <- sample(nrow(sex.list))
    sex.list.group <- sex.list[rows, ]
    
    bird.list.group <- bird.list %>% 
      filter(combogroupID == unique(df$groupID)) %>% 
      mutate(perm_sex =  sex.list.group)

    perm_data <- df %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("actor" = "Color")) %>%
      rename(actor_perm_sex = perm_sex) %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("subject" = "Color")) %>%
      rename(subject_perm_sex = perm_sex)

    perm_data <- perm_data %>%
    mutate(perm_dyad = ifelse(
      actor_perm_sex == subject_perm_sex, "same sex", "opposite sex"
    ))

    perm_summary <- perm_data %>%
      group_by(perm_dyad) %>%
      summarise(mean_events = mean(nevents), .groups = "drop")

   same_sex <- perm_summary$mean_events[perm_summary$perm_dyad == "same sex"]
  opposite_sex <- perm_summary$mean_events[perm_summary$perm_dyad == "opposite sex"]

  perm_results[i, "same sex"] <- ifelse(length(same_sex) == 0, 0, same_sex)
  perm_results[i, "opposite sex"] <- ifelse(length(opposite_sex) == 0, 0, opposite_sex)
  }

par(mfrow=c(1,2))
  
obs_opp <- observed$mean_events[observed$dyad.sex3 == "opposite sex"]
hist(perm_results[, "opposite sex"], main = "Opposite sex", xlab = "Aggression events")
abline(v = obs_opp, lty = 2, col = "red", lwd = 3)
p_low_opp <- (length(which(perm_results[, "opposite sex"] < obs_opp)) + 1) / (t + 1)
p_low_opp
p_high_opp <- (length(which(perm_results[, "opposite sex"] > obs_opp)) + 1) / (t + 1)
p_high_opp


obs_same <- observed$mean_events[observed$dyad.sex3 == "same sex"]
hist(perm_results[, "same sex"], main = "Same sex", xlab = "Aggression events")
abline(v = obs_same, lty = 2, col = "red", lwd = 3)
p_low_same  <- (length(which(perm_results[, "same sex"] < obs_same)) + 1) / (t + 1)
p_low_same 
p_high_same <- (length(which(perm_results[, "same sex"] > obs_same)) + 1) / (t + 1)
p_high_same

return(c(p_low_opp = p_low_opp, p_high_opp = p_high_opp, p_low_same = p_low_same, p_high_same = p_high_same))
}


for (group_name in names(split_dfs_Wrank)) {
jpeg(file.path(figure_output_folder, paste0("perm_dyad_plot_", group_name, ".jpeg")),
     width = 5, height = 5, units = "in", res = 300)
  
this_df <- split_dfs_Wrank[[group_name]]
 
pvals <- dyad_perm(this_df, group_name)
  
dev.off()
  
cat("\nGroup:", group_name, "\n")
  print(pvals)
}
```

### Plot permutation results 2 dyads of five groups

```{r plot permutation 2 dyads}

set.seed(123)

perm2_dev_df <- data.frame()

sex.list <- c("Female", "Female","Female","Female","Female",
              "Male", "Male","Male","Male","Male")

sex.list <- as.data.frame(sex.list)


for (i in seq_along(split_dfs_Wrank)) {

  this_df <- split_dfs_Wrank[[i]]
  group_name <- unique(this_df$groupID)
  
  observed <- this_df %>%
    group_by(dyad.sex3) %>%
    summarise(mean_events = mean(nevents), .groups = "drop")
  
  obs_same <- observed$mean_events[observed$dyad.sex3 == "same sex"]
  obs_opp  <- observed$mean_events[observed$dyad.sex3 == "opposite sex"]
  
  t <- 5000
  perm_results <- matrix(0, nrow = t, ncol = 2)
  colnames(perm_results) <- c("same sex", "opposite sex")
  
  for (i in 1:t) {
     rows <- sample(nrow(sex.list))
    sex.list.group <- sex.list[rows, ]
    
    bird.list.group <- bird.list %>% 
      filter(combogroupID == unique(this_df$groupID)) %>% 
      mutate(perm_sex =  sex.list.group)
    
    perm_data <- this_df %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("actor" = "Color")) %>%
      rename(actor_perm_sex = perm_sex) %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("subject" = "Color")) %>%
      rename(subject_perm_sex = perm_sex) %>%
      mutate(perm_dyad = ifelse(actor_perm_sex == subject_perm_sex,
                                "same sex", "opposite sex"))
    
    perm_summary <- perm_data %>%
      group_by(perm_dyad) %>%
      summarise(mean_events = mean(nevents), .groups = "drop")
    
    perm_results[i, "same sex"] <- ifelse("same sex" %in% perm_summary$perm_dyad,
                                          perm_summary$mean_events[perm_summary$perm_dyad=="same sex"], NA)
    perm_results[i, "opposite sex"] <- ifelse("opposite sex" %in% perm_summary$perm_dyad,
                                              perm_summary$mean_events[perm_summary$perm_dyad=="opposite sex"], NA)
  }

  perm2_dev_df <- rbind(perm2_dev_df,
                       data.frame(
                         group = group_name,
                         dyad_type = "same sex",
                         deviation = obs_same - perm_results[, "same sex"],
                         obs = obs_same,
                         perm = perm_results[, "same sex"]
                       ),
                       data.frame(
                         group = group_name,
                         dyad_type = "opposite sex",
                         deviation = obs_opp - perm_results[, "opposite sex"],
                         obs = obs_opp,
                         perm = perm_results[, "opposite sex"]
                       ))
}

perm2_dev_df %>% 
  group_by(group, dyad_type) %>% 
  summarise(
    obs_val = first(obs),
    prop_lower = mean(first(obs) <= perm)*100,
    prop_higher = mean(first(obs) >= perm)*100,
    mean = mean(perm),
    q75 = quantile(perm, 0.75),
    q25 = quantile(perm, 0.25),
    max = max(perm),
    min = min(perm),
    .groups = "drop"
  )

p_labels <- data.frame(
  group = c("G2","G3"),
  dyad_type = c("opposite sex", "opposite sex"),
  label = c("p = 0.020", "p = 0.025"),
  y = c(5, 5)  
)

facet_labels <- data.frame(
  dyad_type = c("opposite sex", "same sex"),
  label = c("A", "B")
)

dyad2_violin <- ggplot(perm2_dev_df,
                       aes(x = factor(group), y = deviation, fill = factor(dyad_type))) +
  geom_violin(alpha = 0.5, width = 1) +  
  facet_wrap(~dyad_type, nrow = 1, ncol = 2) +
  scale_fill_manual(values = colrs3) + 
  geom_text(
    data = facet_labels, aes(x = -Inf, y = Inf, label = label), inherit.aes = FALSE,
    fontface = "bold", size = 6, hjust = -0.8, vjust = 1) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed", size = 1) +

 geom_text(data = p_labels, aes(x = factor(group), y = y, label = label),inherit.aes = FALSE,size = 3)+

  labs(x = "", y = "Observed mean - permutation mean", fill = "Dyad type") +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 13),
    axis.text.x = element_text(size = 13),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    legend.position = "bottom"#,
    #plot.margin = margin(10, 50, 10, 50)
    )+
  scale_x_discrete(
                   labels = c("G1","G2", "G3", "G4", "G5" )) +
    theme(strip.text = element_text(size = 13, face = "bold"))+
   theme(
    panel.grid.major = element_blank() ,
    panel.grid.minor = element_blank()
  )+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.ticks.y = element_line(color = "black"),
  axis.line.x.bottom = element_line(color = "black"),
  axis.ticks.x = element_line(color = "black"),
  axis.line = element_blank())

dyad2_violin
  
ggsave(file.path(figure_output_folder, "dyad2_violin.tiff"), 
       dyad2_violin, 
       device = "tiff", 
       width = 18, height = 10, units = "cm")

```


## 4 dyad types

```{r permutation 4 dyads, fig.width=5, fig.height=5}

set.seed(123)
dyad_perm <- function(df, group_name){

  observed <- df %>%
    group_by(dyad.sex1) %>%
    summarise(mean_events = mean(nevents), .groups = "drop")

  t <- 5000
  perm_results <- matrix(0, nrow = t, ncol = 4)
  colnames(perm_results) <- c("FF", "FM", "MF", "MM")

  for (i in 1:t) {
   rows <- sample(nrow(sex.list))
    sex.list.group <- sex.list[rows, ]
    
    bird.list.group <- bird.list %>% 
      filter(combogroupID == unique(this_df$groupID)) %>% 
      mutate(perm_sex =  sex.list.group)
    
    perm_data <- this_df %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("actor" = "Color")) %>%
      rename(actor_perm_sex = perm_sex) %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("subject" = "Color")) %>%
      rename(subject_perm_sex = perm_sex) %>%
      mutate(perm_dyad = paste(actor_perm_sex, subject_perm_sex, sep = "-"))

    perm_summary <- perm_data %>%
      group_by(perm_dyad) %>%
      summarise(mean_events = mean(nevents), .groups = "drop")

  FF <- perm_summary$mean_events[perm_summary$perm_dyad == "Female-Female"]
  FM <- perm_summary$mean_events[perm_summary$perm_dyad == "Female-Male"]
  MF <- perm_summary$mean_events[perm_summary$perm_dyad == "Male-Female"]
  MM <- perm_summary$mean_events[perm_summary$perm_dyad == "Male-Male"]

  perm_results[i, "FF"] <- ifelse(length(FF) == 0, 0, FF)
  perm_results[i, "FM"] <- ifelse(length(FM) == 0, 0, FM)
  perm_results[i, "MF"] <- ifelse(length(MF) == 0, 0, MF)
  perm_results[i, "MM"] <- ifelse(length(MM) == 0, 0, MM)
  }

par(mfrow=c(2,2))

obs_MM <- observed$mean_events[observed$dyad.sex1 == "male-male"]
hist(perm_results[, "MM"], main = "MM dyad", xlab = "Aggression events")
abline(v = obs_MM, lty=2, col="red", lwd=3)

#one sided p values on both ends
p_low_MM <- (length(which(perm_results[, "MM"] < obs_MM)) + 1) / (t + 1)
p_low_MM
p_high_MM <- (length(which(perm_results[, "MM"] > obs_MM)) + 1) / (t + 1)
p_high_MM

obs_FF <- observed$mean_events[observed$dyad.sex1 == "female-female"]
hist(perm_results[, "FF"], main = "FF dyad", xlab = "Aggression events")
abline(v = obs_FF, lty=2, col="red", lwd=3)
p_low_FF <- (length(which(perm_results[, "FF"] < obs_FF)) + 1) / (t + 1)
p_low_FF
p_high_FF <- (length(which(perm_results[, "FF"] > obs_FF)) + 1) / (t + 1)
p_high_FF


obs_FM <- observed$mean_events[observed$dyad.sex1 == "female-male"]
hist(perm_results[, "FM"], main = "FM dyad", xlab = "Aggression events")
abline(v = obs_FM, lty=2, col="red", lwd=3)
p_low_FM <- (length(which(perm_results[, "FM"] < obs_FM)) + 1) / (t + 1)
p_low_FM
p_high_FM <- (length(which(perm_results[, "FM"] > obs_FM)) + 1) / (t + 1)
p_high_FM

obs_MF <- observed$mean_events[observed$dyad.sex1 == "male-female"]
hist(perm_results[, "MF"], main = "MF dyad", xlab = "Aggression events")
abline(v = obs_MF, lty=2, col="red", lwd=3)
p_low_MF <- (length(which(perm_results[, "MF"] < obs_MF)) + 1) / (t + 1)
p_low_MF
p_high_MF <- (length(which(perm_results[, "MF"] > obs_MF)) + 1) / (t + 1)
p_high_MF

#two sided p values
perm_centered_MF <- perm_results[, "MF"] - mean(perm_results[, "MF"])
obs_centered_MF  <- obs_MF - mean(perm_results[, "MF"])
p_two_MF <- (length(which(abs(perm_centered_MF) >= abs(obs_centered_MF))) + 1) / (t + 1)


mtext(group_name, side = 3, line = -2, outer = TRUE)

return(c(p_low_MM = p_low_MM, p_high_MM = p_high_MM, 
         p_low_FF = p_low_FF, p_high_FF = p_high_FF,
         p_low_FM = p_low_FM, p_high_FM = p_high_FM, 
         p_low_MF = p_low_MF, p_high_MF = p_high_MF))
}

for (group_name in names(split_dfs_Wrank)) {
jpeg(file.path(figure_output_folder, paste0("perm_dyad4_plot_", group_name, ".jpeg")),
     width = 5, height = 5, units = "in", res = 300)
  
this_df <- split_dfs_Wrank[[group_name]]
 
pvals <- dyad_perm(this_df, group_name)
  
dev.off()
  
cat("\nGroup:", group_name, "\n")
  print(pvals)
}

```


### Plot permutation results 4 dyads of five groups

```{r plot permutation 4 dyads}

perm4_dev_df <- data.frame()


for (i in seq_along(split_dfs_Wrank)) {

  this_df <- split_dfs_Wrank[[i]]
  group_name <- unique(this_df$groupID)
  
  observed <- this_df %>%
    group_by(dyad.sex1) %>%
    summarise(mean_events = mean(nevents), .groups = "drop")
  
  obs_MM <- observed$mean_events[observed$dyad.sex1 == "male-male"]
  obs_FF <- observed$mean_events[observed$dyad.sex1 == "female-female"]
  obs_FM <- observed$mean_events[observed$dyad.sex1 == "female-male"]
  obs_MF <- observed$mean_events[observed$dyad.sex1 == "male-female"]
  
  t <- 5000
  perm_results <- matrix(0, nrow = t, ncol = 4)
  colnames(perm_results) <- c("FF", "FM", "MF", "MM")

  
  for (i in 1:t) {
    rows <- sample(nrow(sex.list))
    sex.list.group <- sex.list[rows, ]
    
    bird.list.group <- bird.list %>% 
      filter(combogroupID == unique(this_df$groupID)) %>% 
      mutate(perm_sex =  sex.list.group)
    
    perm_data <- this_df %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("actor" = "Color")) %>%
      rename(actor_perm_sex = perm_sex) %>%
      left_join(bird.list.group %>% select(Color, perm_sex), by = c("subject" = "Color")) %>%
      rename(subject_perm_sex = perm_sex) %>%
      mutate(perm_dyad = paste(actor_perm_sex, subject_perm_sex, sep = "-"))
    
    perm_summary <- perm_data %>%
      group_by(perm_dyad) %>%
      summarise(mean_events = mean(nevents), .groups = "drop")

  FF <- perm_summary$mean_events[perm_summary$perm_dyad == "Female-Female"]
  FM <- perm_summary$mean_events[perm_summary$perm_dyad == "Female-Male"]
  MF <- perm_summary$mean_events[perm_summary$perm_dyad == "Male-Female"]
  MM <- perm_summary$mean_events[perm_summary$perm_dyad == "Male-Male"]

  perm_results[i, "FF"] <- ifelse(length(FF) == 0, 0, FF)
  perm_results[i, "FM"] <- ifelse(length(FM) == 0, 0, FM)
  perm_results[i, "MF"] <- ifelse(length(MF) == 0, 0, MF)
  perm_results[i, "MM"] <- ifelse(length(MM) == 0, 0, MM)
  }
  

  perm4_dev_df <- rbind(perm4_dev_df,
                       data.frame(
                         group = group_name,
                         dyad_type = "FF",
                         obs = obs_FF,
                         deviation =  obs_FF - perm_results[, "FF"],
                         perm = perm_results[, "FF"]
                       ),
                       data.frame(
                         group = group_name,
                         dyad_type = "FM",
                         obs = obs_FM,
                         deviation = obs_FM - perm_results[, "FM"],
                         perm = perm_results[, "FM"]
                       ),
                       data.frame(
                         group = group_name,
                         dyad_type = "MM",
                         obs = obs_MM,
                         deviation = obs_MM - perm_results[, "MM"],
                         perm = perm_results[, "MM"]
                       ),
                       data.frame(
                         group = group_name,
                         dyad_type = "MF",
                         obs = obs_MF,
                         deviation = obs_MF - perm_results[, "MF"],
                         perm = perm_results[, "MF"]
                       ))
}

 perm4_dev_df %>% 
  group_by(group, dyad_type) %>% 
  summarise(
    obs_val = first(obs),
    prop_lower = mean(perm < first(obs))*100,
    prop_higher = mean(perm > first(obs))*100,
    mean = mean(perm),
    q75 = quantile(perm, 0.75),
    q25 = quantile(perm, 0.25),
    max = max(perm),
    min = min(perm),
    .groups = "drop"
  )

colrs2 <- c("FM"="#a6611a", 
            "MF"="#dfc27d", 
            "FF"="#80cdc1", 
            "MM"="#018571")

perm4_dev_df %>% 
  group_by(group) %>% 
  filter(dyad_type=="FF") %>% 
  summarise(max = max(deviation),
            min = min(deviation))

facet_labels4 <- data.frame(
  dyad_type = c("female-male", "male-female", "female-female", "male-male"),
  label = c("A", "B", "C", "D")
)

perm4_dev_df <- perm4_dev_df %>% 
  mutate(
    dyad_type = case_when(
      dyad_type == "FM" ~ "female-male",
      dyad_type == "MF" ~ "male-female",
      dyad_type == "FF" ~ "female-female",
      dyad_type == "MM" ~ "male-male"
    )
  )

colrs4 <- c("female-male"="#a6611a", 
            "male-female"="#dfc27d", 
            "female-female"="#80cdc1", 
            "male-male"="#018571")
  
#p_labels4 <- data.frame(
# group = c("G3","G5"),
# dyad_type = c("male-male", "male-male"),
# label = c("p = 0.059", "p = 0.070"),
# y = c(-15, -15)  )

dyad4_violin <- ggplot(perm4_dev_df,
                       aes(x = factor(group), y = deviation, fill = factor(dyad_type))) +
  geom_violin(alpha = 0.5,  width = 1) +            
  facet_wrap(~factor(dyad_type, c("female-male", "male-female", "female-female", "male-male")), nrow = 2, ncol = 2) +
    theme_minimal()+
  scale_fill_manual(values = colrs4) + 
  geom_text(
    data = facet_labels4, aes(x = -Inf, y = Inf, label = label), inherit.aes = FALSE,
    fontface = "bold", size = 6, hjust = -0.8, vjust = 1) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed", size = 1) +
 # geom_text(data = p_labels4, aes(x = factor(group), y = y, label = label),inherit.aes = FALSE,size = 3)+
  labs(x = "", y = "Observed mean - permutation mean", fill = "Dyad type") +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 13),
    axis.text.x = element_text(size = 13),
    axis.text.y = element_text(size = 10),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    legend.position = "bottom"
    )+
  scale_x_discrete(
                   labels = c("G1","G2", "G3", "G4", "G5" )) +
    theme(strip.text = element_text(size = 13, face = "bold")) +
   theme(
    panel.grid.major = element_blank() ,
    panel.grid.minor = element_blank()
  )+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.ticks.y = element_line(color = "black"),
  axis.line.x.bottom = element_line(color = "black"),
  axis.ticks.x = element_line(color = "black"),
  axis.line = element_blank()
)

dyad4_violin

ggsave(file.path(figure_output_folder, "dyad4_violin.tiff"), 
       dyad4_violin, 
       device = "tiff", 
       width = 18, height =13, units = "cm")

```


#3. Group level


##Plot rank vs. sex - all five group together 
```{r plot rank and sex,fig.width=10, fig.height=5}

summary(rank_df_all$power)

power_sex_model_boxplot_all <- 
  ggboxplot(rank_df_all, x = "sex", y = "power", color = "sex", add = "jitter") +
  scale_color_manual(values = colrs) + 
  labs(y = "Power score", x = "") +
  theme_minimal() +
  theme(legend.position="none") +
  theme(
    axis.title.y = element_text(size = 16),
    axis.text.y = element_text(size = 13),
    axis.text.x = element_text(size = 16)
  )+
   theme(
    panel.grid.major = element_blank() ,
    panel.grid.minor = element_blank()
  )+
   theme(
  axis.line.y.left = element_line(color = "black"),
  axis.line.x.bottom = element_line(color = "black"),
  axis.ticks = element_line(color = "black"),
  axis.line = element_blank()
)

power_sex_model_boxplot_all

ggsave(file.path(figure_output_folder, "power_sex_model_boxplot_all.tiff"), 
       power_sex_model_boxplot_all, 
       device = "tiff", 
       width = 10, height = 10, units = "cm")

```


##Analysis
LM - 5 groups all together
```{r group lm all together, fig.width=5}

power_sex_model_all <- lmer(power ~ sex + (1 | groupID), data = rank_df_all)
summary(power_sex_model_all)


#groupID does not explain variance, and thus simplified model

power_sex_model_all <- lm(power ~ sex, data = rank_df_all)
summary(power_sex_model_all)

r2(power_sex_model_all)

performance::check_singularity(power_sex_model_all)

power_sex_model_all_summary <- capture.output(summary(power_sex_model_all))
writeLines(power_sex_model_all_summary, file.path(table_output_folder, "power_sex_model_all_summary.txt"))

doc <- read_docx()
for(line in power_sex_model_all_summary){doc <- body_add_par(doc, line, style = "Normal")}
print(doc,target = file.path(table_output_folder,"power_sex_model_all_summary.docx"))

summary(power_sex_model_all)$coefficients %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Predictor") %>% 
  flextable::flextable() %>% 
  flextable::colformat_double(digits = 3) %>% 
  flextable::add_footer_lines(
    "Estimate = coefficient; Std. Error = standard error; z value = t statistic; Pr(>|z|) = p-value."
  ) %>% 
  flextable::autofit() %>% 
  flextable::save_as_docx(
    path = file.path(table_output_folder, "power_sex_model_all_estimates.docx")
  )


#check the model

power_sex_model_all_diagnostics_plot <- check_model(power_sex_model_all, title_size = 8, base_size =7) 
power_sex_model_all_diagnostics_plot

# saving the plot
tiff(file = file.path(figure_output_folder, "power_sex_model_all_diagnostics.tiff"), 
     width = 18, height = 18, units = "cm", res = 300)

print(power_sex_model_all_diagnostics_plot)

dev.off()

```

LM - 5 groups separately
```{r group separate model }
shapiro.test(rank_df_all$power) #Normality violation
bartlett.test(power~ groupID, data = rank_df_all)


power_sex_lm <- function(df) {
  
df1 <- df %>%
  select(birdID = actor, rank = actor.rank, power = actor.power)

df2 <- df %>%
  select(birdID = subject, rank = subject.rank, power = subject.power)

rank_df <- bind_rows(df1, df2) %>%
  distinct(birdID, rank, power) %>% 
  left_join(bird.list %>% select(Color, Sex), by = c("birdID" = "Color")) 

power_sex_model <- lm(power ~ Sex, data = rank_df)
check <- check_model(power_sex_model)
print(check) 
return(power_sex_model)
}

model_summaries <- list()

for (group_name in names(split_dfs_Wrank)) {
  this_df <- split_dfs_Wrank[[group_name]]
  model <- power_sex_lm(this_df)
  model_summaries[[group_name]] <- tbl_regression(model,pvalue_fun = ~ style_pvalue(.x, digits = 2)) %>% 
      bold_labels() %>%
  italicize_levels() %>%
  remove_row_type(variables = everything(), type = "reference", level_value = NULL) %>% 
    modify_table_body(~ .x %>%
                      mutate(
                        label = case_when(
                          label == "Male" ~ "Male (vs. female)",
                          TRUE ~ label))) 
    
}


combined_df <- imap_dfr(
  model_summaries,
  function(tbl, group_name) {

    tbl$table_body %>%
      filter(label == "Male (vs. female)") %>%   # keep only effect row
      mutate(Group = group_name, .before = 1)
  }
)

combined_df <- combined_df %>%
  mutate(
    Group = paste0("G", match(Group, names(model_summaries)))
  ) 

combined_df <- combined_df %>%
  select(Group, estimate, conf.low, conf.high, p.value) %>% 
  mutate(across(where(is.numeric), ~ signif(.x, 2)))

combined_df


flextable(combined_df) %>% 
  save_as_docx( path = paste0(table_output_folder,"/power_sex_model_group_summary.docx"))

```


## Plots of continous aggression events and ordinal social rankings


```{r plot hierarchy}
names(split_dfs_Wrank) <- c("G1","G2","G3", "G4", "G5")
        
plot_group_hierarchy <- function(df, group_name) {
  
ntotal <-  df %>% summarise(ntotal = sum(nevents))

el <- df%>% 
  group_by(actor, subject, actor.sex, subject.sex, power.diff, rank.diff, dyad.sex3) %>% 
  mutate(prop.agg=nevents/ntotal$ntotal) %>%  #number and proportion of aggression events by dyad type 3 (opposite/same sex)
  select(actor, subject, actor.sex, subject.sex, power.diff, rank.diff, dyad.sex3, nevents, prop.agg)

df1 <- df %>%
  select(birdID = actor, rank = actor.rank, power = actor.power)

df2 <- df %>%
  select(birdID = subject, rank = subject.rank, power = subject.power)

rank_df <- bind_rows(df1, df2) %>%
  distinct(birdID, rank, power)

atts <- inner_join(el, rank_df, join_by("actor" == "birdID")) 

atnet <- graph_from_data_frame(
  el,
  directed = TRUE
)


V(atnet)$power <- atts$power[match(V(atnet)$name, atts$actor)]
V(atnet)$rank <- atts$rank[match(V(atnet)$name, atts$actor)]
V(atnet)$sex <- atts$actor.sex[match(V(atnet)$name, atts$actor)]

# Add conditional color, based on direction of aggression
E(atnet)[dyad.sex3=="same sex"]$dcolor <- adjustcolor("chocolate", alpha = 0.4)
E(atnet)[dyad.sex3=="opposite sex"]$dcolor <- adjustcolor("dimgray", alpha = 0.4)
E(atnet)$edge.curved <- ifelse(E(atnet)$dyad.sex3 == "same sex",
                               0.2,   # curve above
                              -0.2)   # curve below

# Set custom attribute-ordered network layout
y <- V(atnet)$power
x <- 1
birdID <- V(atnet)$name
attord<- cbind.data.frame(birdID, x, y) #attribute-ordered layout of nodes

# Add node color pattern by sex
colrs <- c("#F8766D", "#00BFC4")
names(colrs) <- c("Female", "Male")
V(atnet)$color <- colrs[V(atnet)$sex]

#Add text box
pad_x <- 0.03
pad_y <- 0.005

par(mar = c(2, 4.5, 2, 0))
#par(mar = c(1.5,6,2,0))   # tighten margins

plot(NULL, 
     #xlim=c(1,1), 
     xlim=c(0.8, 1.2),
     ylim=c(0,2), 
     ylab="Power score", xlab="",
     cex.axis=1,
     cex.lab=2,
     axes = FALSE,
     xaxt = "n")
#box()
axis(1, at = 1, cex.axis=1, label = FALSE)
axis(2, at = seq(0,2, 0.25),las=1,  cex.axis=1.3)
abline(v = 1, lwd=1.5, col = "black")

# Set node size, label size, tie width
nodesize<-4 #set node size
edge.multiplier <- 100
edge.minimum <- 0.25
tiewidth <- (E(atnet)$prop.agg*edge.multiplier)+edge.minimum #set edge width
labelsize<-0.5 #set node label size

#plot network
plot.igraph(atnet,
add=TRUE,
rescale=FALSE, asp = 0,
layout=attord[,2:3],#sets as attribute-ordered layout, defined above
vertex.size=nodesize, #this references the node circle size, set above
vertex.label = "", #sets node label colors (ids) to black
vertex.color=V(atnet)$color, #sets node fill color by sex
edge.width=tiewidth, #this references the edge width, set above
edge.arrow.size=0.01, #this makes the arrows on the ends of the edges very small
edge.curved=E(atnet)$edge.curved,   
edge.loop.angle=0,
edge.color= E(atnet)$dcolor, #this sets the edge color, based on the colors set above
axes=TRUE,
#xlim=c(1,1),
xlim=c(0.8, 1.2),
ylim=c(-0.25,2.5)
)
text(x=1.05, y=0, label=paste0("N = ", ntotal$ntotal), adj = c(0,0), font = 3, cex=2, pch = 100)
title(main = group_name, cex.main = 3)

}



tiff(file.path(figure_output_folder, "hierarchy_all_groups.tiff"),
     width=25, height=25, units="cm", res=300)

ncol <- 3
nrow <- 2

par(mfrow = c(nrow, ncol),
    mar = c(2, 2, 2, 1), 
    oma = c(2, 2, 2, 2)) 

for (group_name in names(split_dfs_Wrank)) {
  this_df <- split_dfs_Wrank[[group_name]]
  plot_group_hierarchy(this_df, group_name)
}

plot.new()   

legend(x = 0, y = 0.7, legend = c("Female", "Male"), pch = 21, pt.bg = c("#F8766D", "#00BFC4"), title = "Sex", bty = "n",cex = 2)

legend(x = 0, y = 0.4, legend = c("same sex", "opposite sex"), col = c("chocolate", "dimgray"),lwd = 2, title = "Dyad types", bty = "n", cex = 2)

dev.off()



```